---
title: "4.1_data_cleaning"
author: "Borka Domsodi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE)

# Set working directory
setwd("~/my_computer/my_folder") # Replace with local folder path 

# Load packages
library(readxl)
library(tidyverse)
```

### LOAD DATA ###

```{r}
# Select the excel file containing manual user collection
file_path <- file.choose()

# Load Data
manual_data <- read_excel(file_path)

# View Manual Data
head(manual_data)
```

```{r}
# Load user history collected from the Reddit API

# Load Submissions
submission_data <- read_excel("2.1_submissions_data.xlsx")

# View Submissions
head(submission_data)
```

```{r}
# Load Comments
comments_data <- read_excel("2.2_comments_data.xlsx")

# View Comments
head(comments_data)
```

### DEDUPLICATE ###

```{r}
# Submissions

print("Number of rows before deduplication:")
nrow(submission_data)

# Deduplicate
submission_data <- submission_data %>% distinct(url, .keep_all = TRUE)

print("Number of rows after deduplication:")
nrow(submission_data)
```

```{r}
# Comments

print("Number of rows before deduplication:")
nrow(comments_data)

# Deduplicate
comments_data <- comments_data %>% distinct(comment_link, .keep_all = TRUE)

print("Number of rows after deduplication:")
nrow(comments_data)
```

### ASSIGN REAL AUTHORS ###

```{r}
# Search for the author EDPostRequests
post_requests <- submission_data %>% 
  filter(., author=="EDPostRequests")

# Search for benchmark submission IDs
benchmark_submissions <- manual_data %>% 
  filter(., !is.null(submission_id)) %>% 
  select(., user_name, id=submission_id)

# Join the two tables
post_requests <- left_join(post_requests, benchmark_submissions, by="id") 

# Search for those needed to change authors
post_requests <- post_requests %>% 
  filter(!is.na(user_name)) %>% 
  select(., id, user_name)

post_requests
```

```{r}
# Assign real authors
# Anonymized
submission_data$author[which(submission_data$id=="submission_id")] <- "user_name"
submission_data$author[which(submission_data$id=="submission_id")] <- "user_name"
submission_data$author[which(submission_data$id=="submission_id")] <- "user_name"
submission_data$author[which(submission_data$id=="submission_id")] <- "user_name"
submission_data$author[which(submission_data$id=="submission_id")] <- "user_name"
submission_data$author[which(submission_data$id=="submission_id")] <- "user_name"
submission_data$author[which(submission_data$id=="submission_id")] <- "user_name"

# Clean Environment
rm(benchmark_submissions, post_requests)
```

### ASSIGN LABELS ###

```{r}
# Filter data for recovered users
recovered_list <- manual_data %>% 
  filter(., label=="recovered") %>% 
  distinct(user_name)

# Create list from usernames
recovered_list <- as.character(recovered_list$user_name)
```

```{r}
# Filter data for non-recovered users
non_recovered_list <- manual_data %>% 
  filter(., label=="non-recovered") %>% 
  distinct(user_name)

# Create list from usernames
non_recovered_list <- as.character(non_recovered_list$user_name)
```

```{r}
# Create list for both
user_list <- c(recovered_list, non_recovered_list)
user_list <- unique(user_list)
```

```{r}
# Submissions
submission_data$label <- "-"
submission_data$label[which(submission_data$author %in% recovered_list)] <- "recovered"
submission_data$label[which(submission_data$author %in% non_recovered_list)] <- "non-recovered"

# Distribution of label
table(submission_data$label)
```

```{r}
# Comments
comments_data$label <- "-"
comments_data$label[which(comments_data$comment_author %in% recovered_list)] <- "recovered"
comments_data$label[which(comments_data$comment_author %in% non_recovered_list)] <- "non-recovered"

# Distribution of label
table(comments_data$label)
```

### REMOVE DELETED USERS ###

```{r}
# Submissions Data
submission_data <- submission_data %>% 
  filter(., !is.na(author))

# Comments Data
comments_data <- comments_data %>% 
  filter(., !is.na(comment_author))
```

### REVIEW DATA ###

### CHECK 1: is there a user-overlap between the two groups?

```{r}
# Check for overlap
overlap_users <- recovered_list[recovered_list %in% non_recovered_list]
overlap_users2 <- non_recovered_list[non_recovered_list %in% recovered_list]

# Display the overlapping users
print(overlap_users)
print(overlap_users2)
print("There is no overlap between the two lists.")

# Clean Environment
rm(overlap_users, overlap_users2)
```

### CHECK 2: Manually cross-check 5 users of each group and see how many % was collected by the API

```{r}
# Draw a random sample of 5 items from each list
set.seed(1)
recovered_sample <- sample(recovered_list, size = 5, replace = FALSE)
non_recovered_sample <- sample(non_recovered_list, size = 5, replace = FALSE)
sample <- c(recovered_sample, non_recovered_sample)
```

```{r}
# Submissions

# User 1
user <- sample[1]
user_submissions <- submission_data %>% 
  filter(., author==user) %>% 
  select(., author, title, body)

user_submissions
# This user has 1 submission in the dataset, and 1 submission visible in the subreddit.
```

```{r}
# User 2
user <- sample[2]
user_submissions <- submission_data %>% 
  filter(., author==user) %>% 
  select(., author, title, body)

user_submissions
# This user has 1 submission in the dataset, and 1 submission visible in the subreddit.
```

```{r}
# User 3
user <- sample[3]
user_submissions <- submission_data %>% 
  filter(., author==user) %>% 
  select(., author, title, body)

user_submissions
# This user has 1 submission in the dataset, and 1 submission visible in the subreddit.
```

```{r}
# User 4
user <- sample[4]
user_submissions <- submission_data %>% 
  filter(., author==user) %>% 
  select(., author, title, body)

user_submissions
# This user has 2 submissions in the dataset, and 2 submissions visible in the subreddit.
```

```{r}
# User 5
user <- sample[5]
user_submissions <- submission_data %>% 
  filter(., author==user) %>% 
  select(., author, title, body)

user_submissions
# This user has 8 submissions in the dataset, and 4 submissions visible in the subreddit.
```

```{r}
# User 6
user <- sample[6]
user_submissions <- submission_data %>% 
  filter(., author==user) %>% 
  select(., author, title, body)

user_submissions
# This user has 2 submissions in the dataset, and 1 submission visible in the subreddit.
```

```{r}
# User 7
user <- sample[7]
user_submissions <- submission_data %>% 
  filter(., author==user) %>% 
  select(., author, title, body)

user_submissions
# This user has 1 submission in the dataset, and 0 submission visible in the subreddit.
```

```{r}
# User 8
user <- sample[8]
user_submissions <- submission_data %>% 
  filter(., author==user) %>% 
  select(., author, title, body)

user_submissions
# This user has 0 submission in the dataset, and 0 submission visible in the subreddit.
```

```{r}
# User 9
user <- sample[9]
user_submissions <- submission_data %>% 
  filter(., author==user) %>% 
  select(., author, title, body)

user_submissions
# This user has 1 submission in the dataset, and 1 submission visible in the subreddit.
```

```{r}
# User 10
user <- sample[10]
user_submissions <- submission_data %>% 
  filter(., author==user) %>% 
  select(., author, title, body)

user_submissions
# This user has 2 submissions in the dataset, and 1 submission visible in the subreddit.
```

```{r}
# Comments

# User 1
user <- sample[1]
user_comments <- comments_data %>% 
  filter(., comment_author==user) %>% 
  select(., comment_author, comment_body)

user_comments
# This user has 12 comments in the dataset, and 10 comments visible in the subreddit.
```

```{r}
# User 2
user <- sample[2]
user_comments <- comments_data %>% 
  filter(., comment_author==user) %>% 
  select(., comment_author, comment_body)

user_comments
# This user has 1 comment in the dataset, and 1 comment visible in the subreddit.
```

```{r}
# User 3
user <- sample[3]
user_comments <- comments_data %>% 
  filter(., comment_author==user) %>% 
  select(., comment_author, comment_body)

user_comments

# This user has 5 comments in the dataset, and 5 comments visible in the subreddit.
```

```{r}
# User 4
user <- sample[4]
user_comments <- comments_data %>% 
  filter(., comment_author==user) %>% 
  select(., comment_author, comment_body)

user_comments
# This user has 16 comments in the dataset, and 10 comments visible in the subreddit.
```

```{r}
# User 5
user <- sample[5]
user_comments <- comments_data %>% 
  filter(., comment_author==user) %>% 
  select(., comment_author, comment_body)

user_comments
# This user has 116 comments in the dataset, and 63 comments visible in the subreddit.
```

```{r}
# User 6
user <- sample[6]
user_comments <- comments_data %>% 
  filter(., comment_author==user) %>% 
  select(., comment_author, comment_body)

user_comments
# This user has 1 comment in the dataset, and 1 comment visible in the subreddit.
```

```{r}
# User 7
user <- sample[7]
user_comments <- comments_data %>% 
  filter(., comment_author==user) %>% 
  select(., comment_author, comment_body)

user_comments
# This user has 3 comments in the dataset, and 0 comment visible in the subreddit.
```

```{r}
# User 8
user <- sample[8]
user_comments <- comments_data %>% 
  filter(., comment_author==user) %>% 
  select(., comment_author, comment_body)

user_comments
# This user has 3 comments in the dataset, and 2 comments visible in the subreddit.
```

```{r}
# User 9
user <- sample[9]
user_comments <- comments_data %>% 
  filter(., comment_author==user) %>% 
  select(., comment_author, comment_body)

user_comments
# This user has 1 comment in the dataset, and 1 comment visible in the subreddit.
```

```{r}
# User 10
user <- sample[10]
user_comments <- comments_data %>% 
  filter(., comment_author==user) %>% 
  select(., comment_author, comment_body)

user_comments
# This user has 4 comments in the dataset, and 4 comments visible in the subreddit.
```

```{r}
# The dataset seems to be complete

# Clean Environment
rm(user_submissions, user_comments, user, sample, recovered_sample, non_recovered_sample)
```

### CHECK 3: Recovered users -> Newer interactions -> Are they relapsing?

```{r}
# Get benchmark submission ids
benchmark_submissions <- manual_data %>% 
  filter(., label=="recovered" & !is.na(submission_id)) 
benchmark_submissions <- as.character(benchmark_submissions$submission_id)

# Get benchmark submissions
benchmark_submissions <- submission_data %>% 
  filter(., id %in% benchmark_submissions) %>% 
  select(., author, created, body) %>% 
  mutate(type="benchmark submission")

# Get benchmark comment ids
benchmark_comments <- manual_data %>% 
  filter(., label=="recovered" & !is.na(comment_link)) 
benchmark_comments$comment_id <- str_extract(benchmark_comments$comment_link, "(?<=comment/)\\w+")
benchmark_comments <- as.character(benchmark_comments$comment_id)

# Get benchmark comments
benchmark_comments <- comments_data %>% 
  filter(., comment_id %in% benchmark_comments) %>% 
  select(., author=comment_author, created=comment_created, body=comment_body) %>% 
  mutate(type="benchmark comment")

# Create benchmark df
benchmark <- rbind(benchmark_submissions, benchmark_comments)
rm(benchmark_comments, benchmark_submissions)

# Get user list
benchmark_user_list <- as.character(benchmark$author)
```

```{r}
# Add all posts and comments after the benchmark into this dataframe
for (i in benchmark_user_list) {
  
  # Select user's benchmark
  benchmark_created <- benchmark %>% 
    filter(., author==i)
  
  # Extract benchmark date
  benchmark_created <- benchmark_created$created
  
  # Add all submissions after the benchmark date
  x <- submission_data %>% 
    filter(., author==i, created>benchmark_created) %>% 
    select(., author, created, body) %>% 
    mutate(type="submission")
  
  # Add all comments after the benchmark date
  y <- comments_data %>% 
    filter(., comment_author==i, comment_created>benchmark_created) %>% 
    select(., author=comment_author, created=comment_created, body=comment_body) %>% 
    mutate(type="comment")
  
  # Bind these rows to the existing dataframe
  benchmark <- rbind(benchmark, x, y)
}

#Filter out users who only have 1 row in the data frame
benchmark <- benchmark %>%
  group_by(author) %>%
  filter(n() >= 2) %>%
  distinct(body, .keep_all = TRUE) %>% 
  arrange(author, created)

# Clean Environment
rm(benchmark_user_list, i, x, y, benchmark_created)
```

```{r}
# Relapsed users - removing from recovered users
# Anonymized
recovered_list <- recovered_list[recovered_list != c("user_name", "user_name")]
```

### CHECK 4: Non-recovered users -> Newer interactions -> Have they recovered eventually?

```{r}
# Get benchmark submission ids
benchmark_submissions <- manual_data %>% 
  filter(., label=="non-recovered" & !is.na(submission_id)) 
benchmark_submissions <- as.character(benchmark_submissions$submission_id)

# Get benchmark submissions
benchmark_submissions <- submission_data %>% 
  filter(., id %in% benchmark_submissions) %>% 
  select(., author, created, body) %>% 
  mutate(type="benchmark submission")

# Get benchmark comment ids
benchmark_comments <- manual_data %>% 
  filter(., label=="non-recovered" & !is.na(comment_link)) 
benchmark_comments$comment_id <- str_extract(benchmark_comments$comment_link, "(?<=comment/)\\w+")
benchmark_comments <- as.character(benchmark_comments$comment_id)

# Get benchmark comments
benchmark_comments <- comments_data %>% 
  filter(., comment_id %in% benchmark_comments) %>% 
  select(., author=comment_author, created=comment_created, body=comment_body) %>% 
  mutate(type="benchmark comment")

# Create benchmark df
benchmark <- rbind(benchmark_submissions, benchmark_comments)
rm(benchmark_comments, benchmark_submissions)

# Get user list
benchmark_user_list <- as.character(benchmark$author)
```

```{r}
# Add all posts and comments after the benchmark into this dataframe
for (i in benchmark_user_list) {
  
  # Select user's benchmark
  benchmark_created <- benchmark %>% 
    filter(., author==i)
  
  # Extract benchmark date
  benchmark_created <- benchmark_created$created
  
  # Add all submissions after the benchmark date
  x <- submission_data %>% 
    filter(., author==i, created>benchmark_created) %>% 
    select(., author, created, body) %>% 
    mutate(type="submission")
  
  # Add all comments after the benchmark date
  y <- comments_data %>% 
    filter(., comment_author==i, comment_created>benchmark_created) %>% 
    select(., author=comment_author, created=comment_created, body=comment_body) %>% 
    mutate(type="comment")
  
  # Bind these rows to the existing dataframe
  benchmark <- rbind(benchmark, x, y)
}

#Filter out users who only have 1 row in the data frame
benchmark <- benchmark %>%
  group_by(author) %>%
  filter(n() >= 2) %>%
  distinct(body, .keep_all = TRUE) %>% 
  arrange(author, created)

# Clean Environment
rm(benchmark_user_list, i, x, y, benchmark_created)
```

```{r}
# Recovered users - removing from non-recovered users
# Anonymized
non_recovered_list <- non_recovered_list[non_recovered_list != "user_name"]

# Clean Enviornment
rm(benchmark)
```

### REASSIGN LABELS ###

```{r}
# Submissions
submission_data$label <- "-"
submission_data$label[which(submission_data$author %in% recovered_list)] <- "recovered"
submission_data$label[which(submission_data$author %in% non_recovered_list)] <- "non-recovered"

# Distribution of label
table(submission_data$label)
```

```{r}
# Comments
comments_data$label <- "-"
comments_data$label[which(comments_data$comment_author %in% recovered_list)] <- "recovered"
comments_data$label[which(comments_data$comment_author %in% non_recovered_list)] <- "non-recovered"

# Distribution of label
table(comments_data$label)
```

```{r}
# Manual Data
manual_data$label <- "-"
manual_data$label[which(manual_data$user_name %in% recovered_list)] <- "recovered"
manual_data$label[which(manual_data$user_name %in% non_recovered_list)] <- "non-recovered"

# Drop rows
manual_data <- manual_data %>% filter(label != "-")

# Distribution of label
table(manual_data$label)
```

### DISTRIBUTION OF THE TWO GROUPS ###

```{r}
print("Distribution of the two user groups:")
table(manual_data$label)
```

### SAVE FINAL DATA ###

```{r}
# Overwrite Datasets with cleaned
export(submission_data, "2.1_submissions_data.xlsx")
export(comments_data, "2.2_comments_data.xlsx")
```

```{r}
# Save Output
save.image(file="3.1_data_cleaning_output.RData")
```

```{r}
# Clean Global Environment
rm(list = ls())
```

